---
title: "Mean Distance Approximations"
author: "Nicholas \"Kiko\" Whiteley"
output:
  html_document:
    theme: flatly
    code_folding: hide
    df_print: paged
  html_notebook:
    code_folding: hide
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source('setup.R')
```

Obtaining all shortest paths in a graph tends to a time complexity of $\Theta(V^3)$, where $V$ is the total number of vertices in the graph.  Sampling vertices may help give this operation a reasonable runtime on large graphs.

Let $s^2$ be the variance of a sample of $n$ shortest paths in a graph.  Then, the variance of the mean distance of this sample is $s^2/n$.  If $m$ such samples are taken, and those mean distances are then averaged, the variance of this sample of samples is simply $\frac{s^2}{mn}$.

The relative error, then, becomes of large interest.


```{r}
g <- sample_fitness_pl(2e3, 4e3, 2.5)
mean_distance_sample <- function(g, vcount_sample) {
  return(mean(igraph::distances(g,
    v  = sample(1:vcount(g), vcount_sample),
    to = sample(1:vcount(g), vcount_sample)
  )))
}
mean_distance_sample(g, 5)
```


```{r}
samp_vcs <- seq(1, vcount(g), length.out = 10)

mean_distance_for_gnm_size <- function(n) {
  g <- sample_gnm(n, round(2*n))
  return(netrb::mean_distance(g, unconn_dist = diameter(g) + 1))
}
tic()
set.seed(1)
t <- timed_lapply(samp_vcs, 
                  function(vc) mean_distance_sample(g, vc),
                  return_times_only = FALSE,
                  times_run = 1)
toc()
# plot(samp_vcs, t)
t
```
```{r}
y <- pbmclapply(samp_vcs, function(vc) {
  mean_distance_sample(g = g, vcount_sample = vc)
})
plot(samp_vcs, y)
```


```{r}
mean(c(3,Inf,1000))
g <- graphs$ir
n <- vcount(g)
rrn <- round(sqrt(sqrt(n)))

foo <- function(na) {
  d <- igraph::distances(g,
               v =  sample(1:n,rrn),
               to = sample(1:n,rrn))
  d[d == Inf] <- NA
  d[d == 0] <- NA
  return(mean(d, na.rm = TRUE))
}
foo2 <- function(na) {
  md1r <- rep(NA, rrn)
  md1ap <- unlist(pbmclapply(md1r, foo,
                         mc.cores = as.integer(detectCores()-1)))
  return(mean(md1ap))
}
mdx <- foo2(NA)
mdx
```


## Runtime vs. Sampling Fractions
```{r}
g <- graphs$pg
hist(harmonic_centrality(g), breaks = 100)
hist(harmonic_centrality(g,
                         normalized = TRUE),
     breaks = 100)
```



```{r}
xyt <- timed_lapply(samp_vcs, mean_distance_sample, g = g)
plot_Ys_vs_X(xyt, 'x')
```


```{r}
foo <- pbmclapply(
  samp_vcs,
  function(vc) {
    res <- timed_func(function() {
      d <- igraph::distances(
        graph = g,
        v = sample(1:vcount(g), vc),
        to = sample(1:vcount(g), vc)
      )
      d[d == Inf] <- NA
      return(mean(d, na.rm = TRUE))
    },
    return_func_result = TRUE
    )
    print(res$result)
    mds[i] <- res$result
    times[i] <- res$time
    i <- i + 1
    return(res)
  },
  mc.cores = detectCores()
)
toc()
  # cl = cl

# stopCluster(cl)
```

```{r}
set.seed(1)
# g <- sample_gnm(5e2, 1)
# g <- sample_fitness_pl(1e3, 2e3, 2.5)
# g <- graphs$pg
g <- largest_component(g)
d <- diameter(g)
md <- mean(netrb::distances(g), na.rm = TRUE)
md


n <- 20
# md sample repeats
nr <- 4
x1 <- seq(0.01, 0.05, length.out = n)
x2 <- seq(0.01, 0.05, length.out = n)
vs <- matrix(rep(x1,n), nrow=n,ncol=n)
ts <- matrix(rep(x1,n), nrow=n,ncol=n)
es <- matrix(rep(x1,n), nrow=n,ncol=n)
vs <- pbapply(vs, 1, function(x1_i) (x1_i*x2))
ts <- pbapply(ts, 1, function(x1_i) {
  timed_lapply(
    x2,
    function(x2_i) {
      mean_distance_approx(
        g = g,
        vs1 = x2_i,
        vs2 = x1_i,
        times_run = nr
      )
    },
    return_times_only = TRUE
  )
})
es <- pbapply(es, 1, function(x1_i) {
   unlist(mclapply(
    x2,
    function(x2_i) {
      mean_distance_approx_error(
        true_mean_distance = md,
        g   = g,
        vs1 = x2_i,
        vs2 = x1_i,
        times_run = nr
      )
    },
    mc.cores = detectCores() - 1)
  )
})
```

```{r}
ggh <- function(d, lc='white', hc='black') {
  ggplot(reshape2::melt(d), aes(Var1, Var2)) +                           # Create heatmap with ggplot2
  geom_tile(aes(fill = value)) + 
  scale_fill_gradient(low = lc, high = hc)
}
ggh(es, 'green', 'red')
# ggh(ts[1:18,1:18]*es[1:18,1:18], 'green', 'red')

```
```{r}
ggh(ts)
```
