---
title: '`netrb` Simulation Demos'
author: "Nicholas \"Kiko\" Whiteley"
output:
  html_document:
    theme: flatly
    code_folding: hide
    df_print: paged
  html_notebook:
    code_folding: hide
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

source('setup.R')
```

## Mean distance

Take, for example, the Minnesota Roads network:

```{r}
g_mn <- sample_natural_graph('mn')

summary(g_mn)
```

How its mean distance changes as vertices are deleted may be of interest.  One important factor, as mentioned in the ReadMe, is how unconnected distances are treated.

We can plot this metric for deletion order according to, for example, the following vertex attributes:

### Ignoring unconnected distances (`igraph` default)

```{r echo = TRUE}
del_attrs <- c(
  'random',
  'pagerank',
  'close',
  'eigen'
)

mn_md_ignore <- metric_vs_del(
  igraph::mean_distance,
  graph = g_mn,
  del_attrs = del_attrs,
  nchunks = 50
)
```


### Using unconnected distance of $\text{diameter} + 1$


```{r echo = TRUE}

mn_md_unconn_dist <- metric_vs_del(
  netrb::mean_distance,
  unconn_dist = sample_natural_graph_diameter('mn') + 1,
  graph = g_mn,
  del_attrs = del_attrs,
  nchunks = 50
)
```


## Anonymous function

_Note:_ An anonymous function passed as the response metric <u>MUST</u> include a parameter named `graph` unless `pass_graph == FALSE` is passed.  This parameter was named as such to support common `igraph` functions.

Perhaps the size of the largest remaining component, compared to the original number of vertices, is of interest:

Take, for example, the Internet Routers network:

### Size of largest remaining component

```{r echo = TRUE}
g_ir <- sample_natural_graph('ir')

vcount_orig <- vcount(g_ir)

ir_lc <- metric_vs_del(
 graph = g_ir,
 function(graph) {
   lc_size <- vcount(largest_component(graph))
   return(lc_size / vcount_orig)
 },
 del_max = 0.1,
 nchunks = 20,
 del_attrs = c('random', 'pagerank', 'harmonic', 'eigen'),
 plot = FALSE
)
plot_Ys_vs_X(
  ir_lc,
  y_axis_label = 'Size of Largest Remaining Component',
  x_axis_label = 'Vertex Deletions'
)
```
